Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-02 manuscript.Rmd
Trim abstract to 150 words

abstract: |
  Social mobilization requires effective collective coordination. In recent
  years, individuals involved in social movements have taken to social media
  platforms to reach broader audiences at rapid speeds. Effective virtual
  mobilization similarly requires social cohesion and coordination, yet the
  degree to which virtual mobilization reflects or drives real-world movements
  is unclear. Here, we explore the dynamics of real-world events and social
  cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear
  methods cross-recurrence quantification analysis and windowed cross-recurrence
  quantification analysis, we investigate if counts of all daily events, daily
  positive events, and daily negative events are coupled with social cohesion
  found in Syrian tweets. Results indicate that virtual social cohesion is
  coupled with the counts of all and negative events each day but shows a more
  nuanced connection to positive events, only visible when examining
  finer-grained data. This suggests that virtual mobilization does reflect
  real-world movements, with the strongest connections to the frequency of all
  events and the frequency of negative events. We conclude with a discussion of
  implications and applications of nonlinear methods in political science
  research.
  <!-- https://tinyurl.com/ybremelq -->

@@

# plot the time series
ggplot() +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_target, colour = 'all events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_target, colour = 'positive events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_target, colour = 'negative events')) +
  scale_color_manual(values = c("red", "orange", "blue")) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)

@@

# plot the time series
ggplot() +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_source_target, colour = 'all events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_source_target, colour = 'positive events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_source_target, colour = 'negative events')) +
  scale_color_manual(values = c("red", "orange", "blue")) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)

>>>>

abstract: |
  In recent years, individuals involved in social movements have taken to social
  media platforms to reach broader audiences at rapid speeds. Although
  micro-blogging has become a primary means of information dissemination during
  times of turmoil, the degree to which virtual mobilization reflects or drives
  real-world movements is unclear. Here, we explore the dynamics of real-world
  events and Twitter social cohesion in Syria during the Arab Spring. Using the
  nonlinear methods cross-recurrence quantification analysis and windowed
  cross-recurrence quantification analysis, we investigate if frequency of
  events of different intensities are coupled with social cohesion found in
  Syrian tweets. Results indicate that virtual social cohesion is coupled with
  the counts of all and negative events each day but shows a more nuanced
  connection to positive events, suggesting that virtual mobilization does
  reflect real-world movements. We conclude with a discussion of implications
  and applications of nonlinear methods in political science research.
  <!-- https://tinyurl.com/ybremelq -->

@@

# plot the time series
raw_events_ts_target <- ggplot() +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_target, colour = 'all events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_target, colour = 'positive events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_target, colour = 'negative events')) +
  scale_color_manual(values = c("red", "orange", "blue")) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)

@@

# plot the time series
raw_events_ts_source_target <- ggplot() +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=all_events_source_target, colour = 'all events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=pos_events_source_target, colour = 'positive events')) +
  geom_line(event_df, mapping = aes(x= as.Date(Date), y=neg_events_source_target, colour = 'negative events')) +
  scale_color_manual(values = c("red", "orange", "blue")) +
  xlab("Date") +
  ylab("Number of events") +
  ylim(0, 360)
